Summer 2024 Report

### 2024-09-19 Relations/RewritingQs.tex
ARS

>>>>

\section{2024.09.12}
\begin{itemize}
  \item Investigate \texttt{iii-lemma}.  (Is it false, or is there a classical proof?)
  (No constructive proof?)
  \item Look at variations of RP.
  \item What happens if properties involving sequences are reformulated for
  $R^r$? (Cannot decide whether the given sequence is finite or infinite.)
  \item Look at RP- and WCR implies RP!
  \item Can "sequential" properties like RP, RP-, isWFseq, isWFseq-, $\omega$-bounded, etc.,
  be related to the cofinality property.
\end{itemize}
